Live Functional Programming with Typed Holes

### 2018-04-09 calculus.tex
minor

\Figref{fig:bidirectional-typing} defines \emph{bidirectional} typing
%
as two mutually defined judgements: The type synthesis
judgement~$\hsyn{\hGamma}{\hexp}{\htau}$ synthesizes a type $\htau$
for $\hexp$ under typing context $\hGamma$, which tracks typing
assumptions of the form $x : \htau$ in the usual
manner \cite{pfpl,tapl}.
%
The type analysis judgement~$\hana{\hGamma}{\hexp}{\htau}$ checks
expression~$\hexp$ against a given type~$\htau$. Algorithmically, this
type is an output of type synthesis but an input of type analysis. At
the top level, we start with synthesis.

>>>>

\Figref{fig:bidirectional-typing} defines \emph{bidirectional} typing
%
as two mutually defined judgements: The type synthesis
judgement~$\hsyn{\hGamma}{\hexp}{\htau}$ synthesizes a type~$\htau$
for external expression~$\hexp$ under typing context $\hGamma$, which tracks typing
assumptions of the form $x : \htau$ in the usual
manner \cite{pfpl,tapl}.
%
The type analysis judgement~$\hana{\hGamma}{\hexp}{\htau}$ checks
expression~$\hexp$ against a given type~$\htau$. Algorithmically, this
type is an output of type synthesis but an input of type analysis. At
the top level, we start with synthesis.
